---
title: "00_Motion_Detection"
author: "Jackie Kirshenbaum"
date: "1/10/2022; revisited 02/27/2022"
output:
  html_document:
    df_print: paged
  toc: yes
  toc_float: yes
editor_options: 
  chunk_output_type: inline
---

# Loading Libraries

```{r libraries, message=FALSE}
library(tidyverse)
library(foreign)
library(readxl)
library(lubridate)
library(lmerTest)
library(psych)
```

# Read in Pre Data
censor file is a combination of 1s and 0s, where 0s are censored volumes that exhibted >.3mm FD (including the prev vol) and volumes where at least 5% of brain voxels are computed as outliers.

## filepaths

```{r filepaths pre, message=FALSE}
files <- list.files(
  path = "~/Jackie/censor_files_pre.3", all.files = TRUE, full.names = TRUE)
files <- files[-1]
files <- files[-1]


file_subj_name <- list.files(
  path = "~/Jackie/censor_files_pre.3", all.files = FALSE,
full.names = FALSE)


file_comb <- cbind(file_subj_name, files)
```

## selecting subj ids

```{r}
# selecting subject id
c1 <- "censor_"
nchar(c1) # 7
c2 <- "_combined_2.1D" 
nchar(c2) # 14
filename <- 
  file_comb %>%
  data.frame() %>%
  mutate(
    subID = str_sub(file_subj_name, start = 8, end = -15)
  ) %>%
  dplyr::select(subID) %>%
  as.vector()
```

## reading in and unlisting

```{r}
# reading in each 1D file
tbls <- rbind(lapply(file_comb[,2],
  read.delim)
  )

# selecting the 1 column of 0s and 1s
tbl <-
  tbls %>%
  map(1)

# unlisting and converting to df
x <- data.frame(matrix(unlist(tbl), nrow = length(tbl), byrow = TRUE))

# merging subj id name and the motion data
x2 <- cbind(filename, x)
```

# Summing number of censored volumes

```{r}
# 0 = censored vols

cens_df <-
  x2 %>%
  mutate(across(X1:X490, factor),
         subID = factor(subID))

cens_df_long <-
  cens_df %>%
  pivot_longer(cols = X1:X490, names_to = "cens", values_to = "bin") %>%
  group_by(subID, bin) %>%
  summarise(
    n_censored = n()
  ) %>%
  tibble() %>% # adding dummy rows to appropriately compute proprtion of vols censored vs not
  add_row(tibble_row(subID = "sub-HP602", bin = "0", n_censored = 0)) %>%
  add_row(tibble_row(subID = "sub-HP800", bin = "0", n_censored = 0)) %>%
  add_row(tibble_row(subID = "sub-HP813", bin = "0", n_censored = 0)) %>%  
  add_row(tibble_row(subID = "sub-HP815", bin = "0", n_censored = 0)) %>%
  add_row(tibble_row(subID = "sub-HP823", bin = "0", n_censored = 0)) %>%
  add_row(tibble_row(subID = "sub-LP218", bin = "0", n_censored = 0)) %>%
  add_row(tibble_row(subID = "sub-LP244", bin = "0", n_censored = 0)) %>%    
  add_row(tibble_row(subID = "sub-LP254", bin = "0", n_censored = 0)) %>%
  add_row(tibble_row(subID = "sub-LP256", bin = "0", n_censored = 0)) %>%   
  add_row(tibble_row(subID = "sub-LP412", bin = "0", n_censored = 0)) %>%     
  filter(
    bin == "0"
  ) %>%
  mutate(
    perc_cens = n_censored/490
  )

```

# Read in Post Data

## filepaths

```{r filepaths post, message=FALSE}
files_post <- list.files(
  path = "~/Jackie/censor_files_post.3", all.files = TRUE, full.names = TRUE)
files_post <- files_post[-1]
files_post <- files_post[-1]


file_subj_name_post <- list.files(
  path = "~/Jackie/censor_files_post.3", all.files = FALSE,
full.names = FALSE)


file_comb_post <- cbind(file_subj_name_post, files_post)
```

## selecting subj ids

```{r}
# selecting subject id
c1 <- "censor_"
nchar(c1) # 7
c2 <- "_combined_2.1D" 
nchar(c2) # 14
filename_post <- 
  file_comb_post %>%
  data.frame() %>%
  mutate(
    subID = str_sub(file_subj_name_post, start = 8, end = -15)
  ) %>%
  dplyr::select(subID) %>%
  as.vector()
```

## reading in and unlisting

```{r}
# reading in each 1D file
tbls_post <- rbind(lapply(file_comb_post[,2],
  read.delim)
  )

# selecting the 1 column of 0s and 1s
tbl_post <-
  tbls_post %>%
  map(1)

# unlisting and converting to df
x_post <- data.frame(matrix(unlist(tbl_post), nrow = length(tbl_post), byrow = TRUE))

# merging subj id name and the motion data
x2_post <- cbind(filename_post, x_post)
```

# Summing number of censored volumes

```{r}
# 0 = censored vols

cens_df_post <-
  x2_post %>%
  mutate(across(X1:X490, factor),
         subID = factor(subID))

cens_df_post_long <-
  cens_df_post %>%
  pivot_longer(cols = X1:X490, names_to = "cens_post", values_to = "bin_post") %>%
  group_by(subID, bin_post) %>%
  summarise(
    n_censored_post = n()
  ) %>%
  tibble() %>% # adding dummy rows to appropriately compute proprtion of vols censored vs not
  add_row(tibble_row(subID = "sub-HP808", bin_post = "0", n_censored_post = 0)) %>%
  add_row(tibble_row(subID = "sub-HP813", bin_post = "0", n_censored_post = 0)) %>%
  add_row(tibble_row(subID = "sub-HP820", bin_post = "0", n_censored_post = 0)) %>%  
  add_row(tibble_row(subID = "sub-LP254", bin_post = "0", n_censored_post = 0)) %>%
  add_row(tibble_row(subID = "sub-LP404", bin_post = "0", n_censored_post = 0)) %>%
  filter(
    bin_post == "0"
  ) %>%
  mutate(
    perc_cens_post = n_censored_post/490
  )
```

# Combining pre and post motion censor file

```{r}
cens_comb <-
  full_join(
    cens_df_long,
    cens_df_post_long,
    by = "subID"
  ) %>%
  rename(
    n_censored_pre = n_censored,
    perc_cens_pre = perc_cens
  ) %>%
  dplyr::select(-bin, -bin_post)
```

## Exclude?

_denoting whether >XX% frames regressed as outliers_

> 30% of vols, censored at .3mm

```{r}
cens_comb_ex <-
  cens_comb %>%
  mutate(
    exclude_pre =
      ifelse(
        perc_cens_pre > .30| is.na(perc_cens_pre),
        "1",
        "0"
      ),
    exclude_post =
      ifelse(
        perc_cens_post > .30 | is.na(perc_cens_post),
        "1",
        "0"
      ),
    exclude_both =
      ifelse(
        exclude_pre == "1" |
          exclude_post == "1",
        "1",
        "0"
      ),
    Risk =
      ifelse(
        str_detect(subID, "HP"), "high_risk", "low_risk"
      )
    )
```

### Summary

```{r}
cens_comb_ex %>%
  group_by(exclude_both, Risk) %>%
  summarise(
    n = n()
  )
```

## filter those who are excluded  
_either based on motion or not having both pre/post data_  
```{r}
cens_comb_ex %>%
  filter(
    exclude_both == "1"
  ) %>%
  dplyr::select(subID)
```

```{r}
write_csv(cens_comb_ex, "~/Jackie/pre_and_post_excl_ids_.3mm.csv")
```

