---
title: "2_Analysis_brain_change"
author: "Jackie Kirshenbaum"
date: "`r format(Sys.Date(), '%B %e %Y')`"
output:
  html_document:
    df_print: paged
  toc: yes
  toc_float: yes
---

```{r}
options(scipen = 999)
```

# Libraries 

```{r, libraries, message=FALSE}
library(tidyverse)
library(foreign)
library(readxl)
library(lubridate)
library(lmerTest)
library(psych)
library(viridis)
library(hrbrthemes)
library(forcats)
library(DescTools)
library(rstatix)
library(car)
library(ggpubr)
library(robustHD)
library(qwraps2)
library(knitr)
library(lme4)
```

# Read in Data

```{r, filepaths, message=FALSE}
rois_pad_fp <- "~/Jackie/rois_and_pad_usable.csv"
rois_pad <- 
  read_csv(rois_pad_fp)
```


__FU Assessments__  
_Mood and Feelings Questionnaire (MAFQ)_  
>> assesses depressive sx severity over 2 weeks
_Snaith-Hamilton Pleasure Scale (SHAPS)_  
>> sensitivity analysis to anhedonia
_Adolescent Life Events Questionnaire (ALEQ)_  
>> interpersonal and non-interpersonal stress subscales  

1M = _1  
3M = _2  
6M = _3  
9M = _4  
12M = _5  
15M = _6  
18M = _7  
21M = _8  
24M = _9  

## Computing change score

```{r}
rois_change <-
  rois_pad %>%
  mutate(
    subID = factor(subID),
    condition = factor(condition)
  ) %>%
  dplyr::group_by(condition) %>%
  dplyr::mutate(
    # averaging l and r pre and l and r post
    AntIns_avg.pre = (AntIns_l.pre + AntIns_r.pre)/2,
    AntIns_avg.post = (AntIns_l.post + AntIns_r.post)/2,
    NAcc_avg.pre = (NAcc_l.pre + NAcc_r.pre)/2,
    NAcc_avg.post = (NAcc_l.post + NAcc_r.post)/2,
    caudate_avg.pre = (caudate_l.pre + caudate_r.pre)/2,
    caudate_avg.post = (caudate_l.post + caudate_r.post)/2,
    putamen_avg.pre = (putamen_l.pre + putamen_r.pre)/2,
    putamen_avg.post = (putamen_l.post + putamen_r.post)/2,
    # Ant Ins Raw Diff
    AntIns_l_rawdiff = AntIns_l.post - AntIns_l.pre,
    AntIns_r_rawdiff = AntIns_r.post - AntIns_r.pre,
    AntIns_avg_rawdiff = AntIns_avg.post - AntIns_avg.pre,
    # Ant Ins Raw Change
    AntIns_l_rawchange = AntIns_l_rawdiff/AntIns_l.pre,     
    AntIns_r_rawchange = AntIns_r_rawdiff/AntIns_r.pre,  
    AntIns_avg_rawchange = AntIns_avg_rawdiff/AntIns_avg.pre,    
    # dACC Raw Diff
    dACC_rawdiff = dACC.post - dACC.pre,
    # dACC Raw Change
    dACC_rawchange = dACC_rawdiff/dACC.pre,
    # NAcc Raw Diff
    NAcc_l_rawdiff = NAcc_l.post - NAcc_l.pre,
    NAcc_r_rawdiff = NAcc_r.post - NAcc_r.pre,
    NAcc_avg_rawdiff = NAcc_avg.post - NAcc_avg.pre,
    # NAcc Raw Change
    NAcc_l_rawchange = NAcc_l_rawdiff/NAcc_l.pre,
    NAcc_r_rawchange = NAcc_r_rawdiff/NAcc_r.pre,
    NAcc_avg_rawchange = NAcc_avg_rawdiff/NAcc_avg.pre,
    # Caudate Raw Diff
    caudate_l_rawdiff = caudate_l.post - caudate_l.pre,
    caudate_r_rawdiff = caudate_r.post - caudate_r.pre,
    caudate_avg_rawdiff = caudate_avg.post - caudate_avg.pre,
    # Caudate Raw Change
    caudate_l_rawchange = caudate_l_rawdiff/caudate_l.pre,
    caudate_r_rawchange = caudate_r_rawdiff/caudate_r.pre,
    caudate_avg_rawchange = caudate_avg_rawdiff/caudate_avg.pre,
    # Putamen Raw Diff
    putamen_l_rawdiff = putamen_l.post - putamen_l.pre,
    putamen_r_rawdiff = putamen_r.post - putamen_r.pre,
    putamen_avg_rawdiff = putamen_avg.post - putamen_avg.pre,
    # Putamen Raw Change
    putamen_l_rawchange = putamen_l_rawdiff/putamen_l.pre,
    putamen_r_rawchange = putamen_r_rawdiff/putamen_r.pre,
    putamen_avg_rawchange = putamen_avg_rawdiff/putamen_avg.pre
    )

rois_change2 <-
  rois_change %>%
  dplyr::mutate(
    condition = factor(condition)
  ) %>%
  dplyr::group_by(condition) %>%
  mutate(
    NAcc_l.pre_z = as.numeric(scale(NAcc_l.pre)),
    NAcc_l.post_z = as.numeric(scale(NAcc_l.post)),    
    NAcc_r.pre_z = as.numeric(scale(NAcc_r.pre)),
    NAcc_r.post_z = as.numeric(scale(NAcc_r.post)),      
    NAcc_avg.pre_z = as.numeric(scale(NAcc_avg.pre)),
    NAcc_avg.post_z = as.numeric(scale(NAcc_avg.post)),       
    caudate_l.pre_z = as.numeric(scale(caudate_l.pre)),
    caudate_l.post_z = as.numeric(scale(caudate_l.post)),    
    caudate_r.pre_z = as.numeric(scale(caudate_r.pre)),
    caudate_r.post_z = as.numeric(scale(caudate_r.post)),      
    caudate_avg.pre_z = as.numeric(scale(caudate_avg.pre)),
    caudate_avg.post_z = as.numeric(scale(caudate_avg.post)),   
    putamen_l.pre_z = as.numeric(scale(putamen_l.pre)),
    putamen_l.post_z = as.numeric(scale(putamen_l.post)),    
    putamen_r.pre_z = as.numeric(scale(putamen_r.pre)),
    putamen_r.post_z = as.numeric(scale(putamen_r.post)),      
    putamen_avg.pre_z = as.numeric(scale(putamen_avg.pre)),
    putamen_avg.post_z = as.numeric(scale(putamen_avg.post)),
    AntIns_l.pre_z = as.numeric(scale(AntIns_l.pre)),
    AntIns_l.post_z = as.numeric(scale(AntIns_l.post)),    
    AntIns_r.pre_z = as.numeric(scale(AntIns_r.pre)),
    AntIns_r.post_z = as.numeric(scale(AntIns_r.post)),      
    AntIns_avg.pre_z = as.numeric(scale(AntIns_avg.pre)),
    AntIns_avg.post_z = as.numeric(scale(AntIns_avg.post)),       
    dACC.pre_z = as.numeric(scale(dACC.pre)),
    dACC.post_z = as.numeric(scale(dACC.post))    
  )

rois_change2_LOSS <-
  rois_change2 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, dACC.pre_z, dACC.post_z, AntIns_avg.pre_z, AntIns_avg.post_z, AntIns_l.pre_z, AntIns_l.post_z, AntIns_r.pre_z, AntIns_r.post_z)

rois_change2_WIN <-
  rois_change2 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_avg.pre_z, NAcc_avg.post_z, NAcc_l.pre_z, NAcc_l.post_z, NAcc_r.pre_z, NAcc_r.post_z,
                caudate_avg.pre_z, caudate_avg.post_z, caudate_l.pre_z, caudate_l.post_z, caudate_r.pre_z, caudate_r.post_z,
                putamen_avg.pre_z, putamen_avg.post_z, putamen_l.pre_z, putamen_l.post_z, putamen_r.pre_z, putamen_r.post_z)

```

## Creating residualized scores

```{r}
library(modelr)
# dACC
dACC_prepost_resLOSS <- lm(dACC.post_z ~ dACC.pre_z, data = rois_change2_LOSS)
rois_change2_LOSS <-
  rois_change2_LOSS %>% 
  add_residuals(dACC_prepost_resLOSS, var = "dACC_prepost_resLOSS")

# Anterior Insula R
AntIns_r_prepost_resLOSS <- lm(AntIns_r.post_z ~ AntIns_r.pre_z, data = rois_change2_LOSS)

rois_change2_LOSS <-
  rois_change2_LOSS %>% 
  add_residuals(AntIns_r_prepost_resLOSS, var = "AntIns_r_prepost_resLOSS")

# Anterior Insula L
AntIns_l_prepost_resLOSS <- lm(AntIns_l.post_z ~ AntIns_l.pre_z, data = rois_change2_LOSS)

rois_change2_LOSS <-
  rois_change2_LOSS %>% 
  add_residuals(AntIns_l_prepost_resLOSS, var = "AntIns_l_prepost_resLOSS")

# Anterior Insula Avg
AntIns_avg_prepost_resLOSS <- lm(AntIns_avg.post_z ~ AntIns_avg.pre_z, data = rois_change2_LOSS)

rois_change2_LOSS <-
  rois_change2_LOSS %>% 
  add_residuals(AntIns_avg_prepost_resLOSS, var = "AntIns_avg_prepost_resLOSS")

# NAcc R
NAcc_r_prepost_resWIN <- lm(NAcc_r.post_z ~ NAcc_r.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(NAcc_r_prepost_resWIN, var = "NAcc_r_prepost_resWIN")

# NAcc L
NAcc_l_prepost_resWIN <- lm(NAcc_l.post_z ~ NAcc_l.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(NAcc_l_prepost_resWIN, var = "NAcc_l_prepost_resWIN")

# NAcc Avg
NAcc_avg_prepost_resWIN <- lm(NAcc_avg.post_z ~ NAcc_avg.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(NAcc_avg_prepost_resWIN, var = "NAcc_avg_prepost_resWIN")

# caudate R
caudate_r_prepost_resWIN <- lm(caudate_r.post_z ~ caudate_r.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(caudate_r_prepost_resWIN, var = "caudate_r_prepost_resWIN")

# caudate L
caudate_l_prepost_resWIN <- lm(caudate_l.post_z ~ caudate_l.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(caudate_l_prepost_resWIN, var = "caudate_l_prepost_resWIN")

# caudate Avg
caudate_avg_prepost_resWIN <- lm(caudate_avg.post_z ~ caudate_avg.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(caudate_avg_prepost_resWIN, var = "caudate_avg_prepost_resWIN")

# putamen R
putamen_r_prepost_resWIN <- lm(putamen_r.post_z ~ putamen_r.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(putamen_r_prepost_resWIN, var = "putamen_r_prepost_resWIN")

# putamen L
putamen_l_prepost_resWIN <- lm(putamen_l.post_z ~ putamen_l.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(putamen_l_prepost_resWIN, var = "putamen_l_prepost_resWIN")

# putamen Avg
putamen_avg_prepost_resWIN <- lm(putamen_avg.post_z ~ putamen_avg.pre_z, data = rois_change2_WIN)

rois_change2_WIN <-
  rois_change2_WIN %>% 
  add_residuals(putamen_avg_prepost_resWIN, var = "putamen_avg_prepost_resWIN")
```

### Merging back with rest of df
```{r}
rois_change2 <-
  rois_change2 %>%
  mutate(subID = factor(subID),
         condition = factor(condition))
rois_change2_WIN <-
  rois_change2_WIN %>%
  mutate(subID = factor(subID),
         condition = factor(condition)) %>%
  dplyr::select(subID, condition, ends_with("resWIN"))
rois_change2_LOSS <-
  rois_change2_LOSS %>%
  mutate(subID = factor(subID),
         condition = factor(condition)) %>%
  dplyr::select(subID, condition, ends_with("resLOSS"))

rois_change3 <-
  left_join(
    rois_change2,
    rois_change2_LOSS,
    by = c("subID", "condition")
  ) %>%
  mutate(
    subID = factor(subID),
    condition = factor(condition)
  )

rois_change4 <-
  left_join(
    rois_change3,
    rois_change2_WIN,
    by = c("subID", "condition")
  ) %>%
  mutate(
    subID = factor(subID),
    condition = factor(condition)
  )
```

## Distribution of Change scores

### Win Condition

```{r}
rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  pivot_longer(
    cols = c(ends_with("change")),
    names_to = "rois"
  ) %>%
  ggplot(
    aes(x = value)
  ) +
  geom_boxplot() +
  facet_wrap(~rois)

rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  pivot_longer(
    cols = c(ends_with("diff")),
    names_to = "rois"
  ) %>%
  ggplot(
    aes(x = value)
  ) +
  geom_boxplot() +
  facet_wrap(~rois)

rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  pivot_longer(
    cols = c(ends_with("resWIN")),
    names_to = "rois"
  ) %>%
  ggplot(
    aes(x = value)
  ) +
  geom_boxplot() +
  facet_wrap(~rois)

rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  pivot_longer(
    cols = c(ends_with("change")),
    names_to = "rois"
  ) %>%
  group_by(rois) %>%
  summarise(min = min(value),
            max = max(value))

rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  pivot_longer(
    cols = c(ends_with("diff")),
    names_to = "rois"
  ) %>%
  group_by(rois) %>%
  summarise(min = min(value),
            max = max(value))

rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  pivot_longer(
    cols = c(ends_with("resWIN")),
    names_to = "rois"
  ) %>%
  group_by(rois) %>%
  summarise(min = min(value),
            max = max(value))
```

### Loss Condition

```{r}
rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  pivot_longer(
    cols = c(ends_with("change")),
    names_to = "rois"
  ) %>%
  ggplot(
    aes(x = value)
  ) +
  geom_boxplot() +
  facet_wrap(~rois)

rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  pivot_longer(
    cols = c(ends_with("diff")),
    names_to = "rois"
  ) %>%
  ggplot(
    aes(x = value)
  ) +
  geom_boxplot() +
  facet_wrap(~rois)

rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  pivot_longer(
    cols = c(ends_with("resLOSS")),
    names_to = "rois"
  ) %>%
  ggplot(
    aes(x = value)
  ) +
  geom_boxplot() +
  facet_wrap(~rois)

rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  pivot_longer(
    cols = c(ends_with("change")),
    names_to = "rois"
  ) %>%
  group_by(rois) %>%
  summarise(min = min(value),
            max = max(value))

rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  pivot_longer(
    cols = c(ends_with("diff")),
    names_to = "rois"
  ) %>%
  group_by(rois) %>%
  summarise(min = min(value),
            max = max(value))

rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  pivot_longer(
    cols = c(ends_with("resLOSS")),
    names_to = "rois"
  ) %>%
  group_by(rois) %>%
  summarise(min = min(value),
            max = max(value))
```

> wide distribution of change score values due to negative numbers close to zero; thus, using residualized score

# Data Viz

_By Condition and by Pre vs Post_

### WIN CONDITION ###  
caudate, NAcc, putamen

```{r}
rois_win_prepost_viz <- 
  rois_change2 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(-starts_with(c("AntIns", "dACC"))) %>%
  dplyr::select("subID", ends_with(c("pre_z", "post_z"))) %>%
  pivot_longer(
    cols = c(ends_with("pre_z"), ends_with("post_z")),
    names_to = "rois"
  ) %>%
  mutate(
    across(subID:rois, factor),
    value = as.numeric(value)
    )%>%
  separate(., col = "rois", into = c("roi", "timept"), sep = "([.])") %>%
  mutate(roi = factor(roi))
  # spread(roi, value)
```

```{r}

rois_win_prepost_viz$timept = fct_relevel(rois_win_prepost_viz$timept, "pre_z", "post_z")

rois_win_prepost_viz %>%
  dplyr::mutate(
    roi = dplyr::recode(roi, "caudate_l" = "L Caudate", "caudate_r" = "R Caudate",  "NAcc_l" = "L NAcc", "NAcc_r" = "R NAcc", "putamen_l" = "L Putamen", "putamen_r" = "R Putamen") 
    ) %>%
  dplyr::mutate(
    timeptname = recode_factor(timept, pre_z = "Pre-Stress", post_z = "Post-Stress")
    ) %>%
  filter(!grepl('_avg', roi)) %>%
  ggplot(
    aes(x=timeptname, y=value, fill=timeptname)
    ) +
  geom_boxplot(alpha = .5) +
  facet_wrap(~roi) +
  theme_classic() +
  labs(
    x = "Run",
    y = "Beta Value",
    title = "Distribution Activation Based on ROI, and Pre vs. Post Stress for the Win Condition"
  ) + 
  theme(
    axis.text = element_text(size = 10, angle = 90, hjust = 1),
    axis.title = element_text(size = 10),
    title = element_text(size = 10),
    plot.title = element_text(size = 10)
  ) +
  scale_fill_hue(h = c(60,280))
ggsave("prepost_z_win.png", width = 7, height = 7)


## Spaghetti Plots
rois_win_prepost_viz <-
  rois_win_prepost_viz %>%
  dplyr::mutate(
    timeptnum = 
      ifelse(timept == "pre_z", 1, 2)
  )

rois_win_prepost_viz %>%
  dplyr::mutate(
    roi = dplyr::recode(roi, "caudate_l" = "L Caudate", "caudate_r" = "R Caudate",  "NAcc_l" = "L NAcc", "NAcc_r" = "R NAcc", "putamen_l" = "L Putamen", "putamen_r" = "R Putamen")
    ) %>%
  filter(!grepl('_avg', roi)) %>%
  ggplot(
    aes(x=timeptnum, y=value, color = subID)
    ) +
  facet_wrap(~roi) +
  geom_line(alpha = .5) +
  theme_classic() +
  labs(
    x = "Run",
    y = "Beta Value",
    title = "Individual Activation Pre to Post Stress for the Win Condition"
  ) + 
  theme(
    axis.text = element_text(size = 10, angle = 90, hjust = 1),
    axis.title = element_text(size = 10),
    title = element_text(size = 10),
    plot.title = element_text(size = 10)
  ) +
  theme(legend.position="none")
ggsave("ind_prepost_z_win.png", width = 7, height = 7)
```

### LOSS CONDITION ###  
AntIns, dACC

```{r}
rois_loss_prepost_viz <- 
  rois_change2 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(-starts_with(c("NAcc", "caudate", "putamen"))) %>%
  dplyr::select("subID", ends_with(c("pre_z", "post_z"))) %>%
  pivot_longer(
    cols = c(ends_with("pre_z"), ends_with("post_z")),
    names_to = "rois"
  ) %>%
  mutate(
    across(subID:rois, factor),
    value = as.numeric(value)
    )%>%
  separate(., col = "rois", into = c("roi", "timept"), sep = "([.])") %>%
  mutate(roi = factor(roi))
  # spread(roi, value)
```

```{r}

rois_loss_prepost_viz$timept = fct_relevel(rois_loss_prepost_viz$timept, "pre_z", "post_z")

rois_loss_prepost_viz %>%
  dplyr::mutate(
    roi = dplyr::recode(roi, "AntIns_l" = "L Ant Insula", "AntIns_r" = "R Ant Insula")
    ) %>%
  dplyr::mutate(
    timeptname = recode_factor(timept, pre_z = "Pre-Stress", post_z = "Post-Stress")
    ) %>%
  filter(!grepl('_avg', roi)) %>%
  ggplot(
    aes(x=timeptname, y=value, fill=timeptname)
    ) +
  geom_boxplot(alpha = .5) +
  facet_wrap(~roi) +
  theme_classic() +
  labs(
    x = "Run",
    y = "Beta Value",
    title = "Distribution Activation Based on ROI, and Pre vs. Post Stress for the Loss Condition"
  ) + 
  theme(
    axis.text = element_text(size = 10, angle = 90, hjust = 1),
    axis.title = element_text(size = 10),
    title = element_text(size = 10),
    plot.title = element_text(size = 10)
  ) +
  scale_fill_hue(h = c(60,280))
ggsave("prepost_z_loss.png", width = 7, height = 5)


## Spaghetti Plots
rois_loss_prepost_viz <-
  rois_loss_prepost_viz %>%
  dplyr::mutate(
    timeptnum = 
      ifelse(timept == "pre_z", 1, 2)
  )

rois_loss_prepost_viz %>%
  dplyr::mutate(
    roi = dplyr::recode(roi, "AntIns_l" = "L Ant Insula", "AntIns_r" = "R Ant Insula")
    ) %>%
  filter(!grepl('_avg', roi)) %>%
  ggplot(
    aes(x=timeptnum, y=value, color = subID)
    ) +
  facet_wrap(~roi) +
  geom_line(alpha = .5) +
  theme_classic() +
  labs(
    x = "Run",
    y = "Beta Value",
    title = "Individual Activation Pre to Post Stress for the Loss Condition"
  ) + 
  theme(
    axis.text = element_text(size = 10, angle = 90, hjust = 1),
    axis.title = element_text(size = 10),
    title = element_text(size = 10),
    plot.title = element_text(size = 10)
  ) +
  theme(legend.position="none")
ggsave("ind_prepost_z_loss.png", width = 7, height = 5)
```

### T-tests pre and post

```{r}
# WIN

# l NACC
naccl <-
  rois_win_prepost_viz  %>%
  filter(roi == "NAcc_l") %>%
  dplyr::mutate(timept = as.factor(timept)) %>%
  dplyr::ungroup() %>%
  dplyr::select(subID, timept, value)

t.test(value ~ timept, data = naccl)

# r NACC
naccr <-
  rois_win_prepost_viz  %>%
  filter(roi == "NAcc_r") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = naccr)

# l putamen
putamen_l <-
  rois_win_prepost_viz  %>%
  filter(roi == "putamen_l") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = putamen_l)

# r putamen
putamen_r <-
  rois_win_prepost_viz  %>%
  filter(roi == "putamen_r") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = putamen_r)

# l caudate
caudate_l <-
  rois_win_prepost_viz  %>%
  filter(roi == "caudate_l") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = caudate_l)

# r caudate
caudate_r <-
  rois_win_prepost_viz  %>%
  filter(roi == "caudate_r") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = caudate_r)
```

```{r}
# LOSS

# l Ant Ins
antinsl <-
  rois_loss_prepost_viz  %>%
  filter(roi == "AntIns_l") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = antinsl)

# r Ant Ins
antinsr <-
  rois_loss_prepost_viz  %>%
  filter(roi == "AntIns_r") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = antinsr)

# dACC 
dacc <-
  rois_loss_prepost_viz  %>%
  filter(roi == "dACC") %>%
  dplyr::mutate(timept = as.factor(timept))

t.test(value ~ timept, data = dacc)


```

# Identifying Outliers of Change, Difference, and Residualized Scores


## Anterior Insula

```{r}
# Average Change
AntIns_avg_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_avg_rawchange) %>%
  identify_outliers(AntIns_avg_rawchange)  # 8 observations in LOSS (4 are extreme)

AntIns_avg_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_avg_rawdiff) %>%
  identify_outliers(AntIns_avg_rawdiff)  # 1 observations in LOSS (0 extreme)

AntIns_avg_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_avg_prepost_resLOSS) %>%
  identify_outliers(AntIns_avg_prepost_resLOSS)  # 3 observations in LOSS (0 extreme)

# L

AntIns_l_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_l_rawchange) %>%
  identify_outliers(AntIns_l_rawchange)  # 8 observations in LOSS (4 are extreme)

AntIns_l_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_l_rawdiff) %>%
  identify_outliers(AntIns_l_rawdiff)  # 1 observations in LOSS (0 extreme)

AntIns_l_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_l_prepost_resLOSS) %>%
  identify_outliers(AntIns_l_prepost_resLOSS)  # 1 observations in LOSS (0 extreme)

# R

AntIns_r_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_r_rawchange) %>%
  identify_outliers(AntIns_r_rawchange)  # 5 observations in LOSS (3 are extreme)

AntIns_r_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_r_rawdiff) %>%
  identify_outliers(AntIns_r_rawdiff)  # 0 observations in LOSS 

AntIns_r_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, AntIns_r_prepost_resLOSS) %>%
  identify_outliers(AntIns_r_prepost_resLOSS)  # 1 observations in LOSS (0 extreme)
```

## Dorsal Anterior Cingulate

```{r}
dACC_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, dACC_rawchange) %>%
  identify_outliers(dACC_rawchange)  # 14 observations in LOSS (7 are extreme)

dACC_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, dACC_rawdiff) %>%
  identify_outliers(dACC_rawdiff)  # 4 observations in LOSS (0 extreme)

dACC_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(subID, condition, dACC_prepost_resLOSS) %>%
  identify_outliers(dACC_prepost_resLOSS)  # 0 observations in LOSS 

```


## Nucleus Accumbens

```{r}
# Average Change
NAcc_avg_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_avg_rawchange) %>%
  identify_outliers(NAcc_avg_rawchange)  # 10 observations in WIN (6 are extreme)

NAcc_avg_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_avg_rawdiff) %>%
  identify_outliers(NAcc_avg_rawdiff)  # 0 observations in WIN 

NAcc_avg_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_avg_prepost_resWIN) %>%
  identify_outliers(NAcc_avg_prepost_resWIN)  # 3 observations in WIN (0 extreme)

# L

NAcc_l_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_l_rawchange) %>%
  identify_outliers(NAcc_l_rawchange)  # 11 observations in WIN (5 are extreme)

NAcc_l_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_l_rawdiff) %>%
  identify_outliers(NAcc_l_rawdiff)  # 1 observations in WIN (0 extreme)

NAcc_l_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_l_prepost_resWIN) %>%
  identify_outliers(NAcc_l_prepost_resWIN)  # 2 observations in WIN (0 extreme)

# R

NAcc_r_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_r_rawchange) %>%
  identify_outliers(NAcc_r_rawchange)  # 15 observations in WIN (9 are extreme)

NAcc_r_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_r_rawdiff) %>%
  identify_outliers(NAcc_r_rawdiff)  # 2 observations in WIN (0 are extreme)

NAcc_r_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, NAcc_r_prepost_resWIN) %>%
  identify_outliers(NAcc_r_prepost_resWIN)  # 5 observations in WIN (0 extreme)
```

## Caudate

```{r}
# Average change
caudate_avg_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_avg_rawchange) %>%
  identify_outliers(caudate_avg_rawchange)  # 10 observations in WIN (3 are extreme)

caudate_avg_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_avg_rawdiff) %>%
  identify_outliers(caudate_avg_rawdiff)  # 2 observations in WIN (0 extreme)

caudate_avg_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_avg_prepost_resWIN) %>%
  identify_outliers(caudate_avg_prepost_resWIN)  # 1 observations in WIN (0 extreme)

# L

caudate_l_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_l_rawchange) %>%
  identify_outliers(caudate_l_rawchange)  # 5 observations in WIN (3 are extreme)

caudate_l_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_l_rawdiff) %>%
  identify_outliers(caudate_l_rawdiff)  # 1 observations in WIN (0 extreme)

caudate_l_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_l_prepost_resWIN) %>%
  identify_outliers(caudate_l_prepost_resWIN)  # 1 observations in WIN (0 extreme)

# R

caudate_r_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_r_rawchange) %>%
  identify_outliers(caudate_r_rawchange)  # 14 observations in WIN (11 are extreme)

caudate_r_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_r_rawdiff) %>%
  identify_outliers(caudate_r_rawdiff)  # 2 observations in WIN (0 are extreme)

caudate_r_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, caudate_r_prepost_resWIN) %>%
  identify_outliers(caudate_r_prepost_resWIN)  # 1 observations in WIN (0 extreme)
```

## Putamen

```{r}
putamen_avg_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_avg_rawchange) %>%
  identify_outliers(putamen_avg_rawchange)  # 10 observations in WIN (8 are extreme)

putamen_avg_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_avg_rawdiff) %>%
  identify_outliers(putamen_avg_rawdiff)  # 0 observations in WIN 

putamen_avg_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_avg_prepost_resWIN) %>%
  identify_outliers(putamen_avg_prepost_resWIN)  # 1 observations in WIN (0 extreme)

# L

putamen_l_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_l_rawchange) %>%
  identify_outliers(putamen_l_rawchange)  # 15 observations in WIN (9 are extreme)

putamen_l_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_l_rawdiff) %>%
  identify_outliers(putamen_l_rawdiff)  # 0 observations in WIN 

putamen_l_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_l_prepost_resWIN) %>%
  identify_outliers(putamen_l_prepost_resWIN)  # 1 observations in WIN (0 extreme)

# R

putamen_r_outliers_change <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_r_rawchange) %>%
  identify_outliers(putamen_r_rawchange)  # 15 observations in WIN (10 are extreme)

putamen_r_outliers_diff <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_r_rawdiff) %>%
  identify_outliers(putamen_r_rawdiff)  # 0 observations in WIN 

putamen_r_outliers_res <-
  rois_change4 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(subID, condition, putamen_r_prepost_resWIN) %>%
  identify_outliers(putamen_r_prepost_resWIN)  # 1 observations in WIN (0 extreme)
```

## Merging with dataframe 

```{r}
rois_change_iding_outliers <-
  rois_change4 %>%
  dplyr::select(subID, condition, ends_with(".pre"), ends_with(".post"), ends_with(".pre_z"), ends_with(".post_z"), ends_with("rawdiff"), ends_with("rawchange"), ends_with("resWIN"), ends_with("resLOSS")) %>%
  dplyr::mutate(
    subID = factor(subID),
    condition = factor(condition)
    )

# AntIns avg (only extreme outliers)
AntIns_avg_ext_out <-
  AntIns_avg_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(AntIns_avg_is.extreme = is.extreme)

# AntIns l (only extreme outliers)
AntIns_l_ext_out <-
  AntIns_l_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(AntIns_l_is.extreme = is.extreme)

# AntIns r (only extreme outliers)
AntIns_r_ext_out <-
  AntIns_r_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(AntIns_r_is.extreme = is.extreme)

# dACC (only extreme outliers)
dACC_ext_out <-
  dACC_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(dACC_is.extreme = is.extreme)

# NAcc avg (only extreme outliers)
NAcc_avg_ext_out <-
  NAcc_avg_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(NAcc_avg_is.extreme = is.extreme)

# NAcc l (only extreme outliers)
NAcc_l_ext_out <-
  NAcc_l_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(NAcc_l_is.extreme = is.extreme)

# NAcc r (only extreme outliers)
NAcc_r_ext_out <-
  NAcc_r_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(NAcc_r_is.extreme = is.extreme)

# caudate avg (only extreme outliers)
caudate_avg_ext_out <-
  caudate_avg_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(caudate_avg_is.extreme = is.extreme)

# caudate l (only extreme outliers)
caudate_l_ext_out <-
  caudate_l_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(caudate_l_is.extreme = is.extreme)

# caudate r (only extreme outliers)
caudate_r_ext_out <-
  caudate_r_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(caudate_r_is.extreme = is.extreme)

# putamen avg (only extreme outliers)
putamen_avg_ext_out <-
  putamen_avg_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(putamen_avg_is.extreme = is.extreme)

# putamen l (only extreme outliers)
putamen_l_ext_out <-
  putamen_l_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(putamen_l_is.extreme = is.extreme)

# putamen r (only extreme outliers)
putamen_r_ext_out <-
  putamen_r_outliers_change %>%
  dplyr::select(subID, condition, is.extreme) %>%
  filter(is.extreme == TRUE) %>%
  rename(putamen_r_is.extreme = is.extreme)


rois_change_iding_outliers2 <-
  left_join(
    rois_change_iding_outliers,
    AntIns_avg_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers2 <-
  left_join(
    rois_change_iding_outliers2,
    AntIns_l_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers2 <-
  left_join(
    rois_change_iding_outliers2,
    AntIns_r_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers3 <-
  left_join(
    rois_change_iding_outliers2,
    dACC_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers4 <-
  left_join(
    rois_change_iding_outliers3,
    NAcc_avg_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers4 <-
  left_join(
    rois_change_iding_outliers4,
    NAcc_l_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers4 <-
  left_join(
    rois_change_iding_outliers4,
    NAcc_r_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers5 <-
  left_join(
    rois_change_iding_outliers4,
    caudate_avg_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers5 <-
  left_join(
    rois_change_iding_outliers5,
    caudate_l_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers5 <-
  left_join(
    rois_change_iding_outliers5,
    caudate_r_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers6 <-
  left_join(
    rois_change_iding_outliers5,
    putamen_avg_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers6 <-
  left_join(
    rois_change_iding_outliers6,
    putamen_r_ext_out,
    by = c("subID", "condition")
  )
rois_change_iding_outliers6 <-
  left_join(
    rois_change_iding_outliers6,
    putamen_l_ext_out,
    by = c("subID", "condition")
  )
```

## Splitting up by Condtion

```{r}
rois_change_LOSS <-
  rois_change_iding_outliers6 %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(-c(starts_with("NAcc"), starts_with("caudate"), starts_with("putamen")))

rois_change_WIN <-
  rois_change_iding_outliers6 %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(-c(starts_with("AntIns"), starts_with("dACC")))
```


# Write csvs

```{r}
rois_change_LOSS_fp <- "~/Jackie/rois_change_LOSS.csv"
write_csv(rois_change_LOSS, rois_change_LOSS_fp)

rois_change_WIN_fp <- "~/Jackie/rois_change_WIN.csv"
write_csv(rois_change_WIN, rois_change_WIN_fp)
```
