---
title: "Analysis_prepost_shaps"
author: "Jackie Kirshenbaum"
date: "`r format(Sys.Date(), '%B %e %Y')`"
output:
  html_document:
    df_print: paged
  toc: yes
  toc_float: yes
---

# Libraries 

```{r, libraries, message=FALSE}
library(tidyverse)
library(foreign)
library(readxl)
library(lubridate)
library(lmerTest)
library(psych)
library(viridis)
library(hrbrthemes)
library(forcats)
library(DescTools)
library(rstatix)
library(car)
library(ggpubr)
library(robustHD)
library(qwraps2)
library(knitr)
library(lme4)
library(lattice)
library(sjPlot)
library(performance)
library(reghelper)
library(parameters)
library(MuMIn)
```


# Read in Data

```{r, filepaths, message=FALSE}
pad_and_rois_merge_data_fp <- "~/Jackie/pad_and_rois_usable_shaps.csv"
rois_change_LOSS_fp <- "~/Jackie/rois_change_LOSS.csv"
rois_change_WIN_fp <- "~/Jackie/rois_change_WIN.csv"
mfq_fp <- "~/Jackie/pad_and_rois_usable_mafq.csv"

mfq <-
  read_csv(mfq_fp) %>%
  dplyr::select(subID, visit, visitN, mafq_c_w, mafq_c_w_log, condition) %>%
  dplyr::mutate(
    subID = factor(subID),
    visit = factor(visit),
    condition = factor(condition)
  )

pad_and_rois_merge_data <- read_csv(pad_and_rois_merge_data_fp) %>%
    dplyr::mutate(
    subID = factor(subID),
    visit = factor(visit),
    condition = factor(condition),
    masc_c_total = masqharmavoid_c + masqphysical_c + masqsepanx_c + masqsocial_c
  )
pad_and_rois_merge_data <-
  left_join(pad_and_rois_merge_data, mfq, by = c("subID", "visit", "visitN", "condition"))

pad_and_rois_merge_data_WIN <- 
  pad_and_rois_merge_data %>%
  dplyr::mutate(
    subID = factor(subID),
    Group = factor(Group),
    condition = factor(condition)
    ) %>%
  filter(condition == "FB_WIN") %>%
  dplyr::select(-c(ends_with(".pre"), ends_with(".post")))

pad_and_rois_merge_data_LOSS <- 
  pad_and_rois_merge_data %>%
  dplyr::mutate(
    subID = factor(subID),
    Group = factor(Group),
    condition = factor(condition)
    ) %>%
  filter(condition == "FB_LOSS") %>%
  dplyr::select(-c(ends_with(".pre"), ends_with(".post")))

roi_LOSS <-
  read_csv(rois_change_LOSS_fp) %>%
  dplyr::mutate(
    subID = factor(subID),
    condition = factor(condition)
    )  
roi_WIN <-
  read_csv(rois_change_WIN_fp) %>%
  dplyr::mutate(
    subID = factor(subID),
    condition = factor(condition)
    )  

pad_and_rois_merge_WIN <-
  left_join(
    pad_and_rois_merge_data_WIN,
    roi_WIN,
    by = c("subID", "condition")
  )

pad_and_rois_merge_LOSS <-
  left_join(
    pad_and_rois_merge_data_LOSS,
    roi_LOSS,
    by = c("subID", "condition")
  )
```

## z scoring variables
```{r}
pad_and_rois_merge_WIN_z <-
  pad_and_rois_merge_WIN %>%
  dplyr::mutate(
    Group = factor(Group),
    Sex = factor(Sex),
    Age_z = as.numeric(scale(Age)),
    TannerMean_z = as.numeric(scale(TannerMean)),
    aleq_c.L1_z = as.numeric(scale(aleq_c.L1)), # L1 total stress
    aleq_c.L2_z = as.numeric(scale(aleq_c.L2)), # L2 total stress
    aleqNonInt_c.L1_z = as.numeric(scale(aleqNonInt_c.L1)), # L1 non-interpersonal stress
    aleqNonInt_c.L2_z = as.numeric(scale(aleqNonInt_c.L2)), # L2 non-interpersonal stress 
    aleqInt_c.L1_z = as.numeric(scale(aleqInt_c.L1)), # L1 interpersonal stress
    aleqInt_c.L2_z = as.numeric(scale(aleqInt_c.L2)), # L2 interpersonal stress
    visit_num_z = as.numeric(scale(visitN)),
    shaps_c_z = as.numeric(scale(shaps_c)), # anhedonia 
    masc_c_total_z = as.numeric(scale(masc_c_total)), # anxiety total
    mafq_c_w_z = as.numeric(scale(mafq_c_w)), # depression
    mafq_c_w_log_z = as.numeric(scale(mafq_c_w_log)), # logged depression
    NAcc_l_rawdiff_z = as.numeric(scale(NAcc_l_rawdiff)),
    NAcc_r_rawdiff_z = as.numeric(scale(NAcc_r_rawdiff)), 
    NAcc_avg_rawdiff_z = as.numeric(scale(NAcc_avg_rawdiff)),       
    caudate_l_rawdiff_z = as.numeric(scale(caudate_l_rawdiff)),
    caudate_r_rawdiff_z = as.numeric(scale(caudate_r_rawdiff)), 
    caudate_avg_rawdiff_z = as.numeric(scale(caudate_avg_rawdiff)),
    putamen_l_rawdiff_z = as.numeric(scale(putamen_l_rawdiff)),
    putamen_r_rawdiff_z = as.numeric(scale(putamen_r_rawdiff)), 
    putamen_avg_rawdiff_z = as.numeric(scale(putamen_avg_rawdiff)),
    NAcc_l_rawchange_z = as.numeric(scale(NAcc_l_rawchange)),
    NAcc_r_rawchange_z = as.numeric(scale(NAcc_r_rawchange)), 
    NAcc_avg_rawchange_z = as.numeric(scale(NAcc_avg_rawchange)),       
    caudate_l_rawchange_z = as.numeric(scale(caudate_l_rawchange)),
    caudate_r_rawchange_z = as.numeric(scale(caudate_r_rawchange)), 
    caudate_avg_rawchange_z = as.numeric(scale(caudate_avg_rawchange)),
    putamen_l_rawchange_z = as.numeric(scale(putamen_l_rawchange)),
    putamen_r_rawchange_z = as.numeric(scale(putamen_r_rawchange)), 
    putamen_avg_rawchange_z = as.numeric(scale(putamen_avg_rawchange))       
    ) 

contrasts(pad_and_rois_merge_WIN_z$Group) = contr.treatment(2, base = 2)
contrasts(pad_and_rois_merge_WIN_z$Sex) = contr.treatment(2, base = 2)

pad_and_rois_merge_LOSS_z <-
  pad_and_rois_merge_LOSS %>%
  dplyr::mutate(
    Group = factor(Group),
    Sex = factor(Sex),
    Age_z = as.numeric(scale(Age)),
    TannerMean_z = as.numeric(scale(TannerMean)),
    aleq_c.L1_z = as.numeric(scale(aleq_c.L1)), # L1 total stress
    aleq_c.L2_z = as.numeric(scale(aleq_c.L2)), # L2 total stress
    aleqNonInt_c.L1_z = as.numeric(scale(aleqNonInt_c.L1)), # L1 non-interpersonal stress
    aleqNonInt_c.L2_z = as.numeric(scale(aleqNonInt_c.L2)), # L2 non-interpersonal stress 
    aleqInt_c.L1_z = as.numeric(scale(aleqInt_c.L1)), # L1 interpersonal stress
    aleqInt_c.L2_z = as.numeric(scale(aleqInt_c.L2)), # L2 interpersonal stress
    visit_num_z = as.numeric(scale(visitN)),
    shaps_c_z = as.numeric(scale(shaps_c)), # anhedonia
    masc_c_total_z = as.numeric(scale(masc_c_total)), # anxiety total
    mafq_c_w_z = as.numeric(scale(mafq_c_w)), # depression
    mafq_c_w_log_z = as.numeric(scale(mafq_c_w_log)), # logged depression
    AntIns_l_rawdiff_z = as.numeric(scale(AntIns_l_rawdiff)),
    AntIns_r_rawdiff_z = as.numeric(scale(AntIns_r_rawdiff)),    
    AntIns_avg_rawdiff_z = as.numeric(scale(AntIns_avg_rawdiff)),  
    dACC_rawdiff_z = as.numeric(scale(dACC_rawdiff)),        
    AntIns_l_rawchange_z = as.numeric(scale(AntIns_l_rawchange)),
    AntIns_r_rawchange_z = as.numeric(scale(AntIns_r_rawchange)),    
    AntIns_avg_rawchange_z = as.numeric(scale(AntIns_avg_rawchange)),  
    dACC_rawchange_z = as.numeric(scale(dACC_rawchange))  
  )

contrasts(pad_and_rois_merge_LOSS_z$Group) = contr.treatment(2, base = 2)
contrasts(pad_and_rois_merge_LOSS_z$Sex) = contr.treatment(2, base = 2)
```

```{r}
set_theme(
  base = theme_bw()
)
```

# Does brain pre-post stress in the win condition correlate with anhedonia severity 

####  between-person DF

```{r}
pad_and_rois_merge_WIN_z_l2 <-
  pad_and_rois_merge_WIN_z %>%
  dplyr::select(-ends_with(c(".L1", ".L1z"))) %>%
  dplyr::group_by(subID) %>%
  dplyr::mutate(
    mean_shaps = mean(shaps_c, na.rm = TRUE)
  ) %>%
  filter(visitN == 0) 

library(interactions)
```

### NAcc pre-post-stress win
> Three participants were missing up to 10 voxels of coverage in their R NAcc, so this code chucnk also conducts sensitivity analysis excluding those participant.

```{r}

# NAcc_l x within-person stress
mlm_NAcc_l_win_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*NAcc_l_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_NAcc_l_win_prepost_z) # no interaction

# NAcc_r x within-person stress
mlm_NAcc_r_win_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z * NAcc_r_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_NAcc_r_win_prepost_z) # interaction: aleq_c.L1_z:NAcc_r_prepost_resWIN 

hist(pad_and_rois_merge_WIN_z$NAcc_r_prepost_resWIN)
plot_model(mlm_NAcc_r_win_prepost_z, type='diag') 
check_model(mlm_NAcc_r_win_prepost_z) # no outliers
check_collinearity(mlm_NAcc_r_win_prepost_z)

mlm_NAcc_r_win_prepost <- 
  lmer(
    shaps_c ~ 
      Age + Group +  Sex + aleq_c.L2 +  aleq_c.L1*NAcc_r_prepost_resWIN  +
         (1 + visitN | subID), 
       data = pad_and_rois_merge_WIN_z
  )
sjPlot::plot_model(mlm_NAcc_r_win_prepost, type = "int", show.data = TRUE, robust = TRUE, mdrt.values = "meansd")
sim_slopes(mlm_NAcc_r_win_prepost_z, pred=aleq_c.L1_z, modx=NAcc_r_prepost_resWIN, jnplot=TRUE)

####### Exploratory PRE vs POST for R NAcc ########
exp_nacc_r_pre <-  lmer(shaps_c ~ Age+  Group + Sex + aleq_c.L2 +  aleq_c.L1*NAcc_r.pre_z + (1 + visitN | subID), data = pad_and_rois_merge_WIN_z)
summary(exp_nacc_r_pre)
sjPlot::plot_model(exp_nacc_r_pre, type = "int", show.data = TRUE, robust = TRUE, mdrt.values = "meansd")
exp_nacc_r_post <- lmer(shaps_c_z ~ Age_z +  Group + Sex + aleq_c.L2_z + NAcc_r.pre_z + aleq_c.L1_z*NAcc_r.post_z + (1 + visit_num_z | subID), data = pad_and_rois_merge_WIN_z)
summary(exp_nacc_r_post)

####### Exploratory adjusting for longitudinal MFQ and MASC ####### 
mlm_NAcc_r_win_prepost_z_mfq <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z * NAcc_r_prepost_resWIN  + mafq_c_w_z + 
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_NAcc_r_win_prepost_z_mfq)
plot_model(mlm_NAcc_r_win_prepost_z_mfq, type='diag') 
check_collinearity(mlm_NAcc_r_win_prepost_z_mfq)

mlm_NAcc_r_win_prepost_mfq <- 
  lmer(
    shaps_c ~ 
      Age +  Group + Sex + aleq_c.L2 +  aleq_c.L1 * NAcc_r_prepost_resWIN  + mafq_c_w + 
         (1 + visitN | subID), 
       data = pad_and_rois_merge_WIN_z
  )
# title: "R NAcc Activation Post-Stress Moderates \n Longitudinal Association between Life Stress and Anhedonia"
sjPlot::plot_model(mlm_NAcc_r_win_prepost_mfq, type = "int", show.data = TRUE, colors = "Dark2", dot.size = 1, robust = TRUE, mdrt.values = "meansd", title = "", legend.title ="Residualized R NAcc \n Post-Pre Acute Stress")
save_plot("RNaccxStress-Anhedonia.png", fig = ggplot2::last_plot(), width = 12, height = 8, dpi = 300, theme = ggplot2::theme_get(), label.color = "black", label.size = 2.4, axis.textsize = 0.8, axis.titlesize = 0.75, legend.textsize = 0.6, legend.titlesize = 0.65, legend.itemsize = 0.5)

sim_slopes(mlm_NAcc_r_win_prepost_z_mfq, pred=aleq_c.L1_z, modx=NAcc_r_prepost_resWIN, jnplot=TRUE)

mlm_NAcc_r_win_prepost_z_masc <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z * NAcc_r_prepost_resWIN  + masc_c_total_z + 
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_NAcc_r_win_prepost_z_masc)
plot_model(mlm_NAcc_r_win_prepost_z_masc, type='diag') 
check_collinearity(mlm_NAcc_r_win_prepost_z_masc)

mlm_NAcc_r_win_prepost_masc <- 
  lmer(
    shaps_c ~ 
      Age +  Group + Sex + aleq_c.L2 +  aleq_c.L1 * NAcc_r_prepost_resWIN  + masc_c_total + 
         (1 + visitN | subID), 
       data = pad_and_rois_merge_WIN_z
  )
sjPlot::plot_model(mlm_NAcc_r_win_prepost_masc, type = "int", show.data = TRUE, colors = "Dark2", dot.size = 1, robust = TRUE, mdrt.values = "meansd", title = "R NAcc Activation Post-Stress Moderates \n Longitudinal Association between Life Stress and Anhedonia", legend.title ="Residualized R NAcc \n Post-Pre Acute Stress")
sim_slopes(mlm_NAcc_r_win_prepost_z_masc, pred=aleq_c.L1_z, modx=NAcc_r_prepost_resWIN, jnplot=TRUE)

#### Sensitivity Excluding HP806, HP809, and LP216 ####
pad_and_rois_merge_WIN_z_sens <-
  pad_and_rois_merge_WIN_z %>%
  dplyr::mutate(
    sens_excl =
      ifelse(
        subID == "sub-HP809" | subID ==  "sub-HP806" | subID == "sub-LP216",
        "1", NA
      )
    ) %>%
  dplyr::select(subID, sens_excl, everything()) %>%
  filter(is.na(sens_excl))

mlm_NAcc_r_win_prepost_z_sens <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z * NAcc_r_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z_sens
  )
summary(mlm_NAcc_r_win_prepost_z_sens) # interaction holds excluding the three participants

mlm_NAcc_r_win_prepost_z_mfq_sens <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z * NAcc_r_prepost_resWIN  + mafq_c_w_z + 
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z_sens
  )
summary(mlm_NAcc_r_win_prepost_z_mfq_sens) # interaction holds excluding the three participants

mlm_NAcc_r_win_prepost_z_masc_sens <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z * NAcc_r_prepost_resWIN  + masc_c_total_z + 
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z_sens
  )
summary(mlm_NAcc_r_win_prepost_z_masc_sens) # interaction holds excluding the three participants
```
> 2 way interaction between R NAcc and stress predicitng anhedonia

# Table 
```{r}
sjPlot::tab_model(
  mlm_NAcc_r_win_prepost_z, 
  mlm_NAcc_r_win_prepost_z_mfq, 
  mlm_NAcc_r_win_prepost_z_masc,
  bootstrap = TRUE,
  iterations = 1000, 
  dv.labels = c("Anhedonia Severity", "Anhedonia Severity", "Anhedonia Severity"), 
  seed = 1234,
  pred.labels =
    c("Intercept", 
      "Age",
      "Risk Group [High]", 
      "Sex [F]", 
      "Between-person Stress", 
      "Within-person Stress", 
      "R NAcc", 
      "Within-person Stress*R NAcc",
      "Depression", 
      "Anxiety"
      ),
  file = "RNAcc_Main_Anhedonia.doc")
```


# Table Removing Observations without full Coverage
```{r}
sjPlot::tab_model(
  mlm_NAcc_r_win_prepost_z_sens, 
  mlm_NAcc_r_win_prepost_z_mfq_sens, 
  mlm_NAcc_r_win_prepost_z_masc_sens, 
  bootstrap = TRUE,
  iterations = 1000, 
  dv.labels = c("Anhedonia Severity", "Anhedonia Severity", "Anhedonia Severity"), 
  seed = 1234,
  pred.labels =
    c("Intercept", 
      "Age",
      "Risk Group [High]", 
      "Sex [F]", 
      "Between-person Stress", 
      "Within-person Stress", 
      "R NAcc", 
      "Within-person Stress*R NAcc",
      "Depression", 
      "Anxiety"
      ),
  file = "RNAcc_anh_control_dep_anx_sensitivity.doc")
```


### Caudate pre-post-stress win
```{r}
# caudate_l x within-person stress 
mlm_caudate_l_win_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*caudate_l_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_caudate_l_win_prepost_z) # no interaction 

# caudate_r x within-person stress
mlm_caudate_r_win_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*caudate_r_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_caudate_r_win_prepost_z) # no interaction
```

> No interaction by stress for caudate

### Putamen pre-post-stress win
```{r}
# putamen_l x within-person stress
mlm_putamen_l_win_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*putamen_l_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_putamen_l_win_prepost_z) # no interaction

# putamen_r x within-person stress
mlm_putamen_r_win_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex  + aleq_c.L2_z +  aleq_c.L1_z*putamen_r_prepost_resWIN  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_WIN_z
  )
summary(mlm_putamen_r_win_prepost_z) # no interaction  

```

> No interaction by stress for putamen

#### MC CORRECTION FOR WIN

```{r}
# l NAcc, r NAcc, l Caudate, r Caudate, l Putamen, r Putamen
pgain <- c(0.290, 0.008, 0.932, 0.876 , 0.610, 0.886)
p.adjust(pgain, method = "fdr", n = length(pgain))
# CORRECTED l NACC: 0.870, r NACC: 0.048, l CAUD: 0.932, r CAUD: 0.932, l PUT: 0.932, r PUT: 0.932
```


# Does brain pre-post stress in the loss condition correlate with anhedonia severity 

#### For between-person assoications

```{r}
pad_and_rois_merge_LOSS_z_l2 <-
  pad_and_rois_merge_LOSS_z %>%
  dplyr::select(-ends_with(c(".L1", ".L1z"))) %>%
  dplyr::group_by(subID) %>%
  dplyr::mutate(
    mean_shaps = mean(shaps_c, na.rm = TRUE)
  ) %>%
  filter(visitN == 0) 
```

### dACC pre-post-stress loss
```{r}
# dACC x within-person stress
mlm_dacc_loss_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*dACC_prepost_resLOSS  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_LOSS_z
  )
summary(mlm_dacc_loss_prepost_z) # No interaction 

```

### AntIns pre-post-stress loss
```{r}
mlm_antins_l_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*AntIns_l_prepost_resLOSS  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_LOSS_z
  )
summary(mlm_antins_l_prepost_z) #  No interaction   

mlm_antins_r_prepost_z <- 
  lmer(
    shaps_c_z ~ 
      Age_z +  Group + Sex + aleq_c.L2_z +  aleq_c.L1_z*AntIns_r_prepost_resLOSS  +
         (1 + visit_num_z | subID), 
       data = pad_and_rois_merge_LOSS_z
  )
summary(mlm_antins_r_prepost_z) #  No interaction
```

# Null Win Model Tables
```{r}
sjPlot::tab_model(
  mlm_NAcc_l_win_prepost_z, 
  mlm_caudate_l_win_prepost_z,
  mlm_caudate_r_win_prepost_z,
  mlm_putamen_l_win_prepost_z,
  mlm_putamen_r_win_prepost_z,
  bootstrap = TRUE,
  iterations = 1000, 
  dv.labels = c("Anhedonia Severity"), 
  seed = 1234,
  pred.labels = 
    c("Intercept",
      "Age",
      "Risk Group [High]",
      "Sex [F]",
      "Between-person Stress", 
      "Within-person Stress",
      "L NAcc",
      "Within-Person Stress* L NAcc",
      "L Caudate",
      "Within-Person Stress* L Caudate",
      "R Caudate",
      "Within-Person Stress* R Caudate",
      "L Putamen",
      "Within-Person Stress* L Putamen",
      "R Putamen",
      "Within-Person Stress* R Putamen"      
      ),
  file = "Anhedonia_NullResults_Win.doc")
```

# Null Loss Model Tables
```{r}
sjPlot::tab_model(
  mlm_dacc_loss_prepost_z,
  mlm_antins_l_prepost_z,
  mlm_antins_r_prepost_z,
  bootstrap = TRUE,
  iterations = 1000,
  dv.labels = c("Anhedonia Severity"), 
  seed = 1234, 
  pred.labels =
    c("Intercept",
      "Age",
      "Risk Group [High]",
      "Sex [F]",
      "Between-person Stress", 
      "Within-person Stress",
      "dACC",
      "Within-Person Stress* dACC",
      "L Anterior Insula",
      "Within-Person Stress* L Anterior Insula",
      "R Anterior Insula",
      "Within-Person Stress* R Anterior Insula"
      ),
  file = "Anhedonia_NullResults_Loss.doc")
```
